---
title: "Week 4 Lab"
author: "Rachel Behm"
date: "January 31, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Packages
```{r}
library(tidyverse)
library(Ecdat)
library(plm)
library(lmtest)
library(car)
```

1. Nonlinear least squares
```{r}
CellGrowth <- read_csv("CellGrowth.csv")


ggplot(CellGrowth, aes(x= Time, y = CellCount)) +geom_point()


# now we gotta find estimates for logistic growth
#N=A/1 + Be^(-rt)
#carrying capacity= around 3.7k
#starting pop= around 2k 
#if N(0) is 2000 what is B? 

BEstimate <- (3700-2000)/2000
#B= 0.85
#to find r-> when exponential? (look at graph)= around 0 to 5 (isolate this to find growth constant)

lag_phase <- CellGrowth %>%
  filter(Time < 5)

#now lets plot to check to make sure the log is linear
ggplot(lag_phase, aes(x=Time,y=log(CellCount))) + geom_point()
#can confirm, looks linear, now lets find slope

lm(log(CellCount)~Time, data= lag_phase)
#tells us the coefficient is 0.1035= r

```

Now lets find model A,B, and r using Gauss-Newton for iterative convergence (non-linear least squares) bia nls()
```{r}

cell_fit<- nls(CellCount~ A/(1+B*exp(-r*Time)),
               start=list(A=3700, B=0.85, r=0.1035),
               data=CellGrowth,
               trace=TRUE)
#we want to find the acutal variables with this function structure. heres our guess for you to start with, use this data
#trace= true shows you the trials

#values on the left are the sq residuals, decrease then stop (thats how it knows its done)
cell_fit

#now we gonna call the coefficients so can store
A<- coef(cell_fit)[1]
#store the first coefficient from cell fit as A (so will change if model changes)
B <- coef(cell_fit)[2]
r<- coef(cell_fit)[3]

#now we wanna plot them and overlay to compare to our guesses

#create a new sequence of time values 
time_seq<- seq(0,20, length =100)
#a sequence from time 0 to time 20 with 100 observations

#now lets plug that into new model with found variables
cell_pred <-A/(1+B*exp(-r*time_seq))

#now bind with time sequence data
pred_df<- data.frame(time_seq, cell_pred)


#lets graph and compare (add another layer - line to show model)
ggplot(CellGrowth, aes(x=Time, y= CellCount)) +
  geom_point(color="blue", size = 3) +
  geom_line(data= pred_df, aes(x=time_seq, y=cell_pred), color= "orange", size=1)
```

Panel regression - first shot

#states= entity var
#time var =year
#dependent var= packs per capita
#outcome var= avg price

```{r}
cigs_panel<- Cigarette %>%
  select(state,year,packpc, avgprs)

ggplot(Cigarette, aes(x = avgprs, y = packpc, group = state)) +
  geom_point(aes(color = state)) +
  geom_smooth(method = "lm", 
              aes(color = state), 
              size = 0.3, 
              se = FALSE)

#average price affecting purchases in similar way (similar slopes)
#now lets back out unobserved

ggplot(Cigarette, aes(x = year, y = packpc, group = state)) +
  geom_point(aes(color = state)) +
  geom_smooth(method = "lm",
              aes(color = state),
              size = 0.3,
              se = FALSE)
#seems like a time-fixed affect but we gotta start with entity fixed


```

Entity fixed effects model (dont change over time)



```{r}
cigs_model <- plm(packpc~avgprs,
                  data=cigs_panel,
                  index= c("state", "year"),
                  model="within")


#within = model fixed effect
#c= combination with
cigs_model

#"when we account for entity fixed effect this is the effect of pack price on avg pack per person"."every 1 increase on price, -0.32545 change on packs per person"

coeftest(cigs_model, vcov = vcovHC(cigs_model, type="HC1"))
#will tell us the error

```

Time fixed effects model (change over time) add it into the model
```{r}
et_cigs_model <- plm(packpc~avgprs,
                    data= cigs_panel,
                    index = c("state","year"),
                    model="within",
                    effect= "twoways")
et_cigs_model

#now lets see if this is actually better via pftest
pFtest(et_cigs_model,cigs_model)
#compare new to old
```

